On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2019-05-07 manuscripts/IEEE/final_submission.tex
up to page 2

The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $A$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.  Moreover, we provide an explicit, computable formula for $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.

@@

Our formulation of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide uniqueness stability even when generating $A$ do not satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $m$.  Moreover, our approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}). We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix). Finally, we discuss in Sec.~\ref{Discussion} theoretical and practical applications of our mathematical observations. 
%The Appendix contains a proof of Lem.~\ref{MainLemma}.

@@

A detailed statement of our results requires that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors. Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.  A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$. We say $\mathcal{H}$ is \textit{$k$-uniform} when in fact $\mathcal{H} \subseteq {[m] \choose k}$. The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}). We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.

@@

Next, we describe a quantitative generalization of the spark condition. The \emph{lower bound} of a real $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}. By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition} then each submatrix formed from $2k$ of its columns or less has a strictly positive lower bound.

We generalize the matrix lower bound for our purposes by considering only the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the closely associated ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ over column indices. Letting $\mathbf{M}_S$ denote the submatrix formed by the columns of $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$ (in the sections that follow, we will write $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$), we define: 
%\begin{align*} 
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
%\end{align*} 
%
%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$. Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$. For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
%\end{align*} 
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
%\end{align*} 
\begin{align}\label{Ldef}
L_\mathcal{H}(\mathbf{M}) := \frac{1}{\sqrt{k}} \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^{|S|} \right\},
\end{align} 
%
writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{We note that \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$} is known in the compressive sensing literature as the asymmetric lower restricted isometry constant for matrices $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}}  As explained previously, by compactness we have $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}. Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$ and, by the same token, any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.

Finally, we mention that a set of vectors sharing a support $S$ are said to be in \emph{general linear position} when any $|S|$ of them form a linearly independent set.

We are now in a position to state our main result, though for expository purposes we will leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eq.~\eqref{Cdef1} of Sec.~\ref{DUT}. We state here once that all of our theorems assume matrices and vectors consist of real numbers.

@@

\begin{theorem}\label{DeterministicUniquenessTheorem}
Fix integers $n, k, m$ and $\overline m$. Let the $n \times m$ matrix $\mathbf{A}$ satisfy $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP. If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ (given by \eqref{Cdef1}) for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:

Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for $i = 0, \ldots, N$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{Cstable}
\|\mathbf{A}_j- \mathbf{BPD}_j\|_2 \leq C_1 \varepsilon \ \ \text{for all } j \in J
\end{align}
%
for some $J$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
% $\overline m - r(\overline m - m)$

Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$ and for all $i \in [N]$:
\begin{align}\label{b-PDa}
%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
\end{align}
%
where $(\mathbf{x}_i)_J$ here represents the subvector formed from restricting to coefficients indexed by $J$. 
\end{theorem}

@@

%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data. As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order. Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} . %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.

@@

The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition. There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
%efficiently computable bounds have been proposed (e.g. the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
fixing $k$ yields polynomial complexity. Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).  Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general, but efficient sub-cases do exist and may be of practical relevance.

@@

\section{EXTRA}
An additional implication of Thm.~\ref{DeterministicUniquenessTheorem} of potential relevance to Prob.~\ref{OptimizationProblem} is the implied lower bound on $L_{2k}(\mathbf{B})$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}. Due to complexity issues, Prob.~\ref{SLCopt} is often solved by first replacing the $\|\cdot\|_0$-norm with the $\|\cdot\|_1$-norm. The compressive sensing literature informs us that sparse codes are in fact stably recoverable via minimization of the $\|\cdot\|_1$-norm provided $L_{2k}(\mathbf{A})$ is large enough. Thm.~\ref{DeterministicUniquenessTheorem} guarantees that for large enough $L_{2k}(\mathbf{A})$, all valid solutions also have the property that their sparse codes can be inferred by minimization of the $\|\cdot\|_1$ norm. Does this matter..?

>>>>

The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $A$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.  Moreover, we provide an explicit, computable expression for $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is linear in desired accuracy $\delta_1, \delta_2$.

@@

Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.  Moreover, our approach incorporates a combinatorial theory for designing generating codes that should be of independent interest.
We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}). We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix). Finally, we discuss in Sec.~\ref{Discussion} theoretical and practical applications of our mathematical observations. 
%The Appendix contains a proof of Lem.~\ref{MainLemma}.

@@

Precise statements of our results require that we first identify some combinatorial criteria on the supports\footnote{Recall a vector $\mathbf{x}$ is said to be \emph{supported} in $S$ when $\mathbf{x} \in \text{\rm span}\{\mathbf{e}_j: j\in S\}$, with $\mathbf{e}_j$ forming the standard column basis.} of sparse vectors. Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$.  A \emph{hypergraph} on vertices $[m]$  is simply any subset $\mathcal{H} \subseteq 2^{[m]}$. We say that $\mathcal{H}$ is \textit{$k$-uniform} when $\mathcal{H} \subseteq {[m] \choose k}$. The \emph{degree} $\deg_\mathcal{H}(i)$ of a node $i \in [m]$ is the number of sets in $\mathcal{H}$ that contain $i$, and we say $\mathcal{H}$ is \emph{regular} when for some $r$ we have $\deg_\mathcal{H}(i) = r$ for all $i$ (given such an $r$, we say $\mathcal{H}$ is \textit{$r$-regular}). We also write $2\mathcal{H} := \{ S \cup S': S, S' \in \mathcal{H}\}$.

@@

We next give a quantitative generalization of the spark condition (\ref{SparkCondition}) to combinatorial subsets of supports. The \emph{lower bound} of an $n \times m$ matrix $\mathbf{M}$ is the largest $\alpha$ with \mbox{$\|\mathbf{M}\mathbf{x}\|_2 \geq \alpha\|\mathbf{x}\|_2$} for all $\mathbf{x} \in \mathbb{R}^m$ \cite{Grcar10}. By compactness of the unit sphere, every injective linear map has a positive lower bound; hence, if $\mathbf{M}$ satisfies \eqref{SparkCondition}, then submatrices formed from $2k$ of its columns or less have strictly positive lower bounds.

We generalize the matrix lower bound for our purposes by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices. Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$, with $\mathbf{M}_\emptyset := \mathbf{0}$.  In the sections that follow, we also set $\bm{\mathcal{M}}_S$ to denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.  We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
%\begin{align*} 
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
%\end{align*} 
%
%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$. Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$. For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
%\end{align*} 
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
%\end{align*} 
\begin{align}\label{Ldef}
L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
\end{align} 
%
writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}

As explained above, compactness implies $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}. Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.  Finally, we say that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.

We are now in a position to state our main result, though for expository purposes we leave the quantity $C_1$ (a function of $\mathbf{A}$, $\mathbf{x}_1, \ldots, \mathbf{x}_N$, and $\mathcal{H}$) undefined until Eqn.~\eqref{Cdef1} of Sec.~\ref{DUT}. All results results below assume real matrices and vectors.

@@

\begin{theorem}\label{DeterministicUniquenessTheorem}
Fix integers $n, k, m$ and $\overline m$. Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}. If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ (given by \eqref{Cdef1}) for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:

Every $n \times \overline m$ matrix $\mathbf{B}$ for which there are $k$-sparse $\mathbf{\overline x}_1, \ldots, \mathbf{\overline x}_N$ satisfying \mbox{$\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon$} for all $i \in [N]$ has $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and an invertible diagonal matrix $\mathbf{D}$ such that:
\begin{align}\label{Cstable}
\|\mathbf{A}_j- \mathbf{BPD}_j\|_2 \leq C_1 \varepsilon, \ \ \text{for all } j \in J,
\end{align}
%
for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}. 
% $\overline m - r(\overline m - m)$

Moreover, if $\mathbf{A}$ satisfies \eqref{SparkCondition} and $\varepsilon < L_{2k}(\mathbf{A}) / C_1$, then $\mathbf{B}$ also satisfies \eqref{SparkCondition} with $L_{2k}(\mathbf{B}\mathbf{PD}) \geq L_{2k}(\mathbf{A}) - C_1 \varepsilon$, and for all $i \in [N]$:
\begin{align}\label{b-PDa}
%\|\mathbf{x}^J_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}^{\overline J}_i\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}^{J}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon \ \  \text{for $i \in [N]$}.
\|(\mathbf{x}_i)_J - (\mathbf{D}^{-1}\mathbf{P}^{\top} \mathbf{\overline x}_i)_J\|_1 &\leq  \left( \frac{ 1+C_1 \|\mathbf{x}_i\|_1 }{ L_{2k}(\mathbf{A}) -  C_1\varepsilon } \right) \varepsilon,
\end{align}
%
where $(\mathbf{x}_i)_J$ represents the subvector formed from restricting to coefficients indexed by $J$. 
\end{theorem}

@@

%\cite{li2004analysis, Georgiev05, Aharon06, Hillar15}
We should stress the point here that framing the problem in terms of hypergraphs has allowed us to show, unlike in previous works on the subject, that the matrix $\mathbf{A}$ need not necessarily satisfy \eqref{SparkCondition} to be recoverable from data. As an example, let $\mathbf{A} = [ \mathbf{e}_1, \ldots, \mathbf{e}_5, \mathbf{v}]$ with $\mathbf{v} = \mathbf{e}_1 + \mathbf{e}_3 + \mathbf{e}_5$ and take $\mathcal{H}$ to be all consecutive pairs of indices $1, \ldots ,6$ arranged in cyclic order. Then for $k=2$, the matrix $\mathbf{A}$ fails to satisfy \eqref{SparkCondition} while still satisfying the first assumptions of Thm.~\ref{DeterministicUniquenessTheorem}.%, hence guaranteeing \eqref{Cstable} . %(since $\{ \mathbf{A}_1, \mathbf{A}_3, \mathbf{A}_5, \mathbf{A}_6\}$ is not a linearly independent set).
%This weakening allows for a practical (polynomial) amount of data to still guarantee a stable dictionary in the case where the set of sparse supports for the $\mathbf{\overline x}_i$ is known to have a size that grows polynomially in $m$ and $k$.

@@

The practically-minded reader should note that the explicit constants $C_1$ and $C_2$ are effectively computable: the quantity $L_k$ may be calculated as the smallest singular value of a certain matrix, while the quantity $\xi$ involves computing ``canonical angles'' between subspaces, which reduce again to an efficient singular value decomposition. There is no known fast computation of $L_k$ in general, however, since even $L_{k} > 0$ is NP-hard \cite{tillmann2014computational}, although 
%efficiently computable bounds have been proposed (e.g. the ``mutual coherence" of a matrix \cite{donoho2003optimally}); alternatively, 
fixing $k$ yields polynomial complexity. Moreover, calculating $C_2$ requires an exponential number of queries to $\xi$ unless $r$ is held fixed, too (e.g., the ``cyclic order'' hypergraphs described above have $r=k$).  Thus, as presented, $C_1$ and $C_2$ are not efficiently computable in general, but efficient subcases do exist and may be of practical relevance.

@@

\section{EXTRA}
An additional implication of Thm.~\ref{DeterministicUniquenessTheorem} of potential relevance to Prob.~\ref{OptimizationProblem} is the implied lower bound on $L_{2k}(\mathbf{B})$ in the case where $\mathbf{A}$ satisfies \eqref{SparkCondition}. Due to complexity issues, Prob.~\ref{SLCopt} is often solved by first replacing the $\|\cdot\|_0$-norm with the $\|\cdot\|_1$-norm. The compressed sensing literature informs us that sparse codes are in fact stably recoverable via minimization of the $\|\cdot\|_1$-norm provided $L_{2k}(\mathbf{A})$ is large enough. Thm.~\ref{DeterministicUniquenessTheorem} guarantees that for large enough $L_{2k}(\mathbf{A})$, all valid solutions also have the property that their sparse codes can be inferred by minimization of the $\|\cdot\|_1$ norm. Does this matter..?
